---
title: "STAT 705 Fall 2018 Final Project"
author: "Jerrison Li Liu"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
---

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r read_data, echo=FALSE}

file_path <- paste0("/Users/jerrison/Wharton_MBA/Wharton_STAT_705/",
                    "assignments/final/",
                    "wait_times_20_to_70_by_5_with_1000_its.csv")

wait_time_data <- read.csv(file_path, header = T, stringsAsFactors = FALSE)

```

# Analysis Results Filename and Number of Iterations

## Filename

The name of the file with the results from the analysis of average wait time
is: \newline **`r basename(file_path)`**.

## Number of Iterations in Analysis

The number of iterations for the analysis was **`r nrow(wait_time_data)`**.

\newpage

# Average Wait Time in Minutes vs. Effort (Number of Cars)

```{r part_c, echo=FALSE}

#c. A plot that shows level of effort (on the x-axis) against estimated average
# wait time on the y-axis.
#   It should also have a horizontal line added at height y = 4, so that an
# optimal level of effort can
#   be visualized. Axes should be labelled appropriately and the plot given a
# title. The commands "plot" and "abline"
#   are enough to make the plot. You don't have to use ggplot2, but you can if
# you want.

library(ggplot2)

mean_wait_time <- (apply(X = wait_time_data, 2, FUN = mean))
mean_wait_time <-
    data.frame(cbind(names(mean_wait_time), mean_wait_time), 
               stringsAsFactors = FALSE)
colnames(mean_wait_time) <- c("effort", "average_wait_minutes")

# pretty up the effort column
mean_wait_time$effort <-
    gsub(pattern = "X",
         replacement = "",
         x = mean_wait_time$effort)


p1 <-
    ggplot(data = mean_wait_time, aes(x = effort,
                                      y = as.numeric(average_wait_minutes))) +
    geom_bar(stat = "identity") +
    geom_hline(yintercept = 4, col = "red") +
    ggtitle("Average Wait Time vs. Effort") +
    ylab("Average Wait Time (Minutes)") +
    xlab("Effort (Number of Cars)") +
    geom_text(x = 9, y = 6, label = "Optimal Level of Effort = 4")


p1

```

\newpage

# 95% Wait Time in Minutes vs. Effort (Number of Cars)

```{r part_d, echo=FALSE}

ninety_five_percentile <- apply(X = wait_time_data, 2, FUN = quantile, probs = 0.95)
ninety_five_percentile <-
    data.frame(cbind(names(ninety_five_percentile), ninety_five_percentile),
               stringsAsFactors = FALSE)
colnames(ninety_five_percentile) <- c("effort", "ninety_five_percentile_wait_minutes")

# pretty up the effort column
ninety_five_percentile$effort <-
    gsub(pattern = "X",
         replacement = "",
         x = ninety_five_percentile$effort)

p2 <-
    ggplot(data = ninety_five_percentile, aes(x = effort,
                                      y = as.numeric(ninety_five_percentile_wait_minutes))) +
    geom_bar(stat = "identity") +
    geom_hline(yintercept = 4, col = "red") +
    ggtitle("95% Percentile Wait Time vs. Effort") +
    ylab("95% Percentile Wait Time (Minutes)") +
    xlab("Effort (Number of Cars)") +
    geom_text(x = 9, y = 6, label = "Optimal Level of Effort = 4")


p2

```

